%1
\FR{Das System kann über \gls{REST} und \gls{HTTPS} bedient werden.}{001}{A}

\FR{Die einzigen Vorraussetzungen zur Benutzung des Webservices soll eine bestehende Internetverbindung, sowie ein aktueller Browser sein.}{001}{A}

\FR{Das System soll die folgenden Browser unterstützen: Firefox ab Version 41, Chrome ab Version 45, Opera 32, Internet Explorer 11}{001}{A}

\FR{Das System soll über iOS ab Version 7.0, sowie über Android ab Version 4.0 über den integrierten Browser des jeweiligen Betriebssystems erreichbar sein.}{018, UR021, UR024}{A}

\FR{Eine spezielle mobile Website muss nicht verfügbar sein}{001}{A}


%2
\FR{Bei gleichen Eingaben sollen gleiche Ergebnisse bzw. Vorhersagen generiert werden.}{002}{A}

\FR{Die Funktionsfähigkeit der nicht vorimplementierten Algorithmen muss durch den \gls{admin} gewährleistet werden.}{002}{A}

\FR{Bei gleichen Eingaben sollen gleiche Ergebnisse bzw. Vorhersagen generiert werden.}{002}{A}


%3
\FR{Das System soll das Hochladen von Daten ermöglichen, sowie das Festsetzen von Berechtigungen für Selbige.}{003}{A}

\FR{Eine Validierung der hochgeladenen Daten ist nicht notwendig.}{003}{A}

\FR{Das System generiert einen eindeutige \gls{URI} für jede Datei, über die der Nutzer auf jene zugreifen kann.}{003}{A}


%4
\FR{Die Datensätze sowie die Auswahl des Algorithmus erfolgt über eine tabellarisch angeordnete Eingabemaske.}{004}{A}

\FR{Die eingegebenen Daten müssen nicht vom System auf ihre Richtigkeit geprüft werden.}{004}{A}


%5
\FR{Das System soll plattformübergreifend einsetzbar sein.}{005}{A}


%6
\FR{Das System soll Java \glspl{Interface} zur Erstellung von \glspl{Plugin} zur Verfügung stellen. Jedes Interface soll mindestens festlegen welche Datensätze das \gls{Plugin} verarbeiten kann und welche Rückgabewerte zu erwarten sind.}{006}{A}


%7
\FR{Das System soll eine Ansicht zur Benutzerverwaltung beinhalten, über die personenbezogene Daten und Einstellungen geändert werden können. Im Falle des \gls{admin} sollen weitere Konfigurationsoptionen für z.B. \glspl{Gast} zur Verfügung gestellt werden.}{007}{A}


%8
\FR{Das System soll eine Ansicht zur Verwaltung der vom Nutzer hochgeladenen Daten beinhalten. Im Falle des \gls{admin} sollen sämtliche Dateien auf dem Sever verwaltet werden können.}{008}{A}


%9
\FR{Das System soll ein Standard \gls{Plugin} für die grafische Ausgabe von Algorithmen beinhalten.}{009}{A}

\FR{Weitere grafische \glspl{Plugin} sollen nach der Überprüfung durch den \gls{admin} in das System integriert werden können.}{009}{A}


%10
\FR{Das System muss \gls{REST} konform sein, um die serverübergreifende Kommunikation zu gewährleisten.}{0010}{A}


%11
\FR{Das System soll die Registrierung von Nutzern über eine gültige E-Mail-Adresse, Benutzername und Passwort ermöglichen.}{011}{A}

\FR{Bei der Registrierung neuer Benutzer soll vorher geprüft werden ob bereits ein Benutzer mit dem angegebenen Name oder der gleichen E-Mail Adresse existiert. Sollte dies zutreffen soll eine entsprechende Fehlermeldung ausgegeben werden.}{011}{A}


%12
\FR{Das System soll einen Gast Benutzer bereitstellen, der gleichzeitig mehrfach verwendet werden kann.}{012}{A}

\FR{Der \gls{Gast} darf keinen Zugriff auf den Menüpunkte zur Verwaltung der Gruppen haben}{012}{A}


%13
\FR{Der \gls{admin} soll über das Einstellungsmenü die Möglichkeit haben die Größe des Datenuploads für \glspl{Gäste} über ein Eingabefeld zu beschränken.}{013}{A}

\FR{Der \gls{admin} soll die Laufzeit von Algorithmen die der \gls{Gast} ausführt über das Einstellungsmenü auf eine definierte Höchstlaufzeit festlegen können. Die Laufzeit muss mindestens 10 Minuten betragen.}{013}{A}


%14
\FR{Der Nutzer soll über das Dateiverwaltungsmenü die Möglichkeit haben neue Pakete zu erstellen. Beim Erstellen des Pakets  soll er die Dateien, die jenes Paket beinhalten soll, auswählen können.}{014}{A}

\FR{Der Nutzer soll in einem Untermenü "Pakete", der Dateiverwaltung, alle öffentlich zugänglichen, sowie seine eigenen Pakete einsehen und herunterladen können.}{014}{A}



%15



%16 



%17
\FR{Monatlich ist das System planmäßig für 10 Minuten nicht erreichbar um Backups zu erstellen.}{017}{A}

\FR{Im Falle eines nicht planmäßigen Ausfalls des Systems soll der \gls{admin} über seine E-Mail-Adresse benachrichtigt werden.}{017}{A}

\FR{Das System soll plattformunabhängig und nicht an spezifische Hardware gebunden sein, um eine schnelle Portierung der Software auf neue Server zu gewährleisten.}{017}{A}


%18



\FR{The system shall give the possibility to record \gls{recordable plugins} while sessions. Therefore the user can select which plugins in a session he wants to record. 
   }{009}{A}

\FR{Every registered user can choose whether he/she can be recorded or not. For an unregistrered user this option shall be set to no recordings.
   }{021}{A}

\FR{The system denies the recording of a plugin if in the session is a user who forbids the recording
   }{021}{A}

\FR{The systems stores records of differnt plugins in several files.
   }{009}{A}

\FR{For an whiteboard recording the system stores every step by drawing - not only the end-result.
   }{009}{A}

\FR{For an text chat the chat history will be stored as plain/text since the recording started.
   }{009}{A}

\FR{For a video recording a video file will be saved since the recording is started.
   }{009}{A}

\FR{For a audio recording the audio file will be saved since the recording started.
   }{009}{A}

\FR{The system have to include the plugin of a digital whiteboard on which users can draw geometrical objects or write text. They can use it on their own or in sessions.
   }{010}{A}

\FR{The system have to give the opportunity to include a whiteboard to a session, that other users in the session can hava a look at the whiteboard or edit the whiteboard too.
   }{010}{A}

\FR{By including the whiteboard to a session the user has to decide whether the members of the session can only see the whiteboard or even edit things.
   }{010}{A}

\FR{The system shall give a user the possibility to have more than one session.
   }{013}{A}

\FR{The system denies a new session if with a new session the quality of the other sessions falls under a well defined value. For video chat this border lies by X kB and by voice chat by Y kB.
   }{013}{A}

\FR{The system devides between three different arts of plugins. The first are high traffic plugins, the secont are medium traffic plugins and the third are less traffic plugins. So the system gives 10 percent of speed to the less traffic plugins, 30 percent to the medium traffic plugins, and 60 percent of speed to the high traffic plugins.
   }{013}{A}

\FR{Every plugin can be marked (but only one at a time) as priorised, so that this plugin gets the most speed of the internet connection and the other plugins only gets the minimal value.
   }{013}{A}

\FR{The system can deny new session who run over the server or
      a file upload if he has overload.
   }{013}{A}

\FR{In a session a user can include a arbitrary number of plugins at the same time. 
   }{014}{A}

\FR{The system have to give the possibillity to add every plugin to a session.
   }{028}{A}

\FR{The User has the possibility to include every opened dock on his flex dock in a session.
   }{012, UR014}{A}

\FR{Every Plugin can have its own window inside the multi window view.
   }{015}{A}

\FR{Sessions or even parts of sessions (Plugins that are storable) can be stored and reloaded from the session admin.
	}{027}{A}

\FR{When a user includes a plugin to a session, the user has to decide which rights the specific users in the session has on the plugin.
	}{023}{A}

\FR{While the session the user who added a plugin to the session (only this user) can change the permissions of the other users.
	}{023}{A}

\FR{The system supports registered and unregistered users. 
	}{023}{A}

\FR{Registered shall be able to store their settings made at previous logins, sessions and able to record plugins. Unregistered user always start with default settings and changes they made
are only valid for their current session. 
	}{020}{A}

\FR{The system provides a Weka plugin where the user must
      specify a dataset in arff format (which have to be located on
      the server where the application is running), parameters and the
      algorithm which shall be used.}{005}{A}

\FR{The system provides an OpenTox plugin which implements the OpenTox \gls{API}.}{005}{A}

\FR{When a user shares his/her screen all rights of other users are temporarily set to readonly.}{006}{A}

\FR{The system includes a version-control-system to provide sharing and editing documents. The user can select and edit the latest version but has the opportunity to open older revision in a readonly mode. When changing a file a new revision is created and uploaded to the server.}{007}{A}

\FR{When two users trying to work simultanously on the same file there are two cases. \\In the case that both users are in the same session they can work simultanously. \\In the other case the user who wants to open the file secondly opens the file in an readonly mode.}{007}{A}

\FR{When a user logs in he/she has got the possibiltiy to add
      other registered users to its adressbook. A user can be added in
      3 ways.\\1. When a user is in a conference he/she can click on
      an other username and select "Add to adressbook".\\2. On every
      users profile there is an option to add these contact to the
      adressbook.\\3. When a user invites someone and this person registers they both appear in each others adressbook.\\Of course users can be removed from an adressbook. There is also the possibillity to organize the contacts in groups.}{011}{A}

\FR{With the addressbook it is possible to invite multiple users in a group with one click to a conference.}{011}{A}

\FR{The system provides a \gls{Flexdock} GUI where the user can freely drag and resize windows. The flexdock is designed that every plugin can have its own dock.}{012, UR015}{A}

\FR{Users can customize the appearance in the user settings.}{016}{A}

\FR{The system makes use of \gls{ICE}. ICE delivers techniques to establish connections to clients even they are behind a firewall or router. }{017}{A}


\FR{The well defined plugin api ensures that every plugin offers ways to handle different rights and views.}{023}{A}

\FR{The system provides a settings area where users can view and change their current settings (background colour, font-size, font, font-colour and if its allowed to record the user) made to the theme and the plugins.}{016}{A}

\FR{The only things which are needed to use the software are an internet-connection and a browser which deals with HTML5 and the webRTC.}{016}{A}

\FR{The system makes the user who first invites another member to a plugin (so he starts a session) to the session admin.}{032}{A}

\FR{The system allows the session admin to give permissions to the session members. These permissions are the right to add plugins or kick and add other users.}{032}{A}

\FR{Every user registered or not is able to invite other people. The only thing he/she needs is a valid email adress to where the invitationlink is sent.}{031}{A}

\FR{The system provides an administration area where the system admin can trigger manual backups and has database access where he/she can update the period between the garbage collection.}{029}{A}